%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.1 2019-11-03
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Additional modifications by:
% Dylan Ashley
%
% Important note:
% This template requires the cv.cls file to be in the same directory as the
% .tex file. The cv.cls file provides the cv style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{cv}

\name{Dylan Ashley}
\address{{\urlstyle{same} +41 78 213 19 50 ~ \\ ~ \href{mailto:mail@dylanashley.io}{mail@dylanashley.io} ~ \\ ~ \url{https://dylanashley.io}}}

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D. in Informatics} \hfill Expected Early 2026 \vspace{0.05em}\\
Universit{\`{a}} della Svizzera italiana (Dalle Molle Institute for Artificial Intelligence Research) \vspace{0.05em}\\
Supervisor: J{\"u}rgen Schmidhuber \vspace{0.05em}\\
Focus: Reinforcement Learning, Neural Networks, Machine Learning

%------------------------------------------------

{\bf M.Sc. in Computing Science} \hfill Nov.\ 2020 \vspace{0.05em}\\
University of Alberta (Alberta Machine Intelligence Institute) \vspace{0.05em}\\
Supervisor: Richard S. Sutton \textbf{(2024 Turing Award Recipient)} \vspace{0.05em}\\
GPA: 4.0 / 4.0

%------------------------------------------------

{\bf B.Sc. Honors in Computing Science} \hfill Jun.\ 2017 \vspace{0.05em}\\
University of Alberta

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Research Scientist Intern}{May.\ 2025 -- Nov.\ 2025}{Meta Platforms, Inc.}
    \item Working at the Z{\"u}rich office under the supervision of Ga{\"e}l Le Lan on Agentic AI.
\end{rSubsection}

\begin{rSubsection}{Visiting Researcher}{Jan.\ 2023 -- May 2025}{Center of Excellence in Generative AI, King Abdullah University of Science and Technology}
    \item Working with Prof.\ Eric Feron and Prof.\ J{\"{u}}rgen Schmidhuber on several topics related to deep learning and robotics.
    \item Co-lead the writing of two successful grants worth US\$ 2'376'300 and US\$ 850'000.
\end{rSubsection}

\begin{rSubsection}{Chief Technology Officer}{May 2021 -- Present}{Perseverance Analytics Ltd.}
    \item Founding member of an incorporated non-profit data science startup based in Alberta, Canada.
    \item Startup focuses on connecting communities to social supports to bridge the gap between the availability and accessibility of services.
\end{rSubsection}

\begin{rSubsection}{Doctoral Research Assistant}{Jan.\ 2021 -- Present}{Universit{\`{a}} della Svizzera italiana}
    \item Working with Prof.\ J{\"{u}}rgen Schmidhuber on several deep learning topics.
\end{rSubsection}

\begin{rSubsection}{Vice-President Academic}{May 2019 -- Apr.\ 2020}{Graduate Students' Association, University of Alberta}
    \item Salaried official representative of over 7,900 graduate students in academic matters.
    \item Advocated for graduate student issues to the university and worked with the university to build a better learning environment for students.
    \item Delivered several significant advocacy victories, including better oversight for mentorship and a reduced increment in tuition during a budgetary crisis.
    \item Time commitment of approximately 30 hours a week for a one-year term.
\end{rSubsection}

\begin{rSubsection}{Graduate Research Assistant}{Sep.\ 2017 -- Aug.\ 2020}{Reinforcement Learning and Artificial Intelligence Lab, University of Alberta}
    \item Worked with Prof.\ Richard S. Sutton and others on several reinforcement learning topics.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Summer Research Assistant}{May.\ 2015 -- Aug.\ 2017}{University of Alberta}
    \item Won three separate competitive four-month NSERC Undergraduate Student Research Awards, the first working with first Prof.\ Jos{\'{e}} Nelson Amaral, and the latter two working with Prof.\ Richard S. Sutton.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PEER-REVIEWED PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Peer-Reviewed Publications}

\begin{rPublications}
    \item
        Zhuge, M., Zhao, C. \textbf{Ashley, D. R.}, Wang, W., Khizbullin, D., Xiong, Y., Liu, Z., Chang, E., Krishnamoorthi, R., Tian, Y., Shi, Y., Chandra, V., \& Schmidhuber, J.
        (2025).
        Agent-as-a-Judge: Evaluate Agents with Agents.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}

        \vspace{-0.4em}
        In press.
        Preprint available at \url{https://arxiv.org/abs/2410.10934}.
    \item
        Wang, Y., Wu, Q., Li, W., \textbf{Ashley, D. R.}, Faccio, F., Huang, C., \& Schmidhuber, J.
        (2025).
        Scaling Value Iteration Networks to 5000 Layers for Extreme Long-Term Planning.
        \textit{Proceedings of the 42nd International Conference on Machine Learning.}

        \vspace{-0.4em}
        In press.
        Preprint available at \url{https://arxiv.org/abs/2406.08404}.
        Previously presented at the 2024 European Workshop on Reinforcement Learning (EWRL).
    \item
        Zhuge, M.$^*$, Liu, H.$^*$, Faccio, F.$^*$, \textbf{Ashley, D. R.}$^*$, Csordas, R., Gopalakrishnan, A., Hamdi, A., Hammoud, H. A. A. K., Herrmann, V., Irie, K., Kirsch, L., Li, B., Li, G., Liu, S., Mai, J., Piekos, P., Ramesh, A., Schlag, I., Shi, W., Stanic, A., Wang, W., Wang, Y., Xu, M., Fan, D.-P., Ghanem, B., \& Schmidhuber, J.
        (2025).
        Mindstorms in natural language-based societies of mind.
        \textit{Computational Visual Media} \textbf{(IF 17.3)}, \textit{11}(1), 29--81.
        \url{https://doi.org/10.26599/CVM.2025.9450460}

        \vspace{-0.4em}
        Previously presented at the NeurIPS 2023 Workshop on Robustness of Zero/Few-Shot Learning in Foundation Models \textbf{(Best-paper Award)}.
    \item
        \textbf{Ashley, D. R.}$^*$, Herrmann, V.$^*$, Friggstad, Z., \& Schmidhuber, J.
        (2025).
        On narrative information and the distillation of stories.
        \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence} \textbf{(IF 20.8)}, \textit{47}(2), 697--707.
        \url{https://doi.org/10.1109/TPAMI.2024.3480702}

        \vspace{-0.4em}
        Previously presented at the NeurIPS 2023 Workshop on Machine Learning for Creativity and Design and at the NeurIPS 2022 Workshop Information-Theoretic Principles in Cognitive Systems.
    \item
        {\v{S}}trupl, M., Faccio, F., \textbf{Ashley, D. R.}, Srivastava, R. K., \& Schmidhuber, J.
        (2022).
        Reward-Weighted Regression Converges to a Global Optimum.
        \textit{Proceedings of the Thirty-Sixth AAAI Conference on Artificial Intelligence,} 8361--8369.
        \url{https://doi.org/10.1609/aaai.v36i8.20811}
    \item
        \textbf{Ashley, D. R.}
        (2020).
        \textit{Understanding Forgetting in Artificial Neural Networks} [Master's thesis, University of Alberta].
        University of Alberta Education and Research Archive.
        \url{https://doi.org/10.7939/r3-6zvv-5z64}
    \item
        \textbf{Ashley, D. R.}$^*$, Chockalingam, V.$^*$, Kuzma, B.$^*$, \& Bulitko, V.
        (2019).
        Learning to Select Mates in Evolving Non-playable Characters.
        \textit{Proceedings of the 2019 IEEE Conference on Games,} 1--8.
        \url{https://doi.org/10.1109/CIG.2019.8848114}
    \item
        \textbf{Ashley, D. R.}$^*$, Chockalingam, V.$^*$, Kuzma, B.$^*$, \& Bulitko, V.
        (2019).
        Learning to Select Mates in Artificial Life.
        \textit{Proceedings of the Genetic and Evolutionary Computation Conference Companion,} 103--104.
        \url{https://doi.org/10.1145/3319619.3322060}
    \item
        Sherstan, C., \textbf{Ashley, D. R.}$^*$, Bennett, B.$^*$, Young, K., White, A., White, M., \& Sutton, R. S.
        (2018).
        Comparing Direct and Indirect Temporal-Difference Methods for Estimating the Variance of the Return.
        \textit{Proceedings of the 34th Conference on Uncertainty in Artificial Intelligence,} 63--72.
        \url{http://auai.org/uai2018/proceedings/papers/35.pdf}
    \item
        Amaral, J. N., Borin, E., \textbf{Ashley, D. R.}, Benedicto, C., Colp, E., Hoffmam, J. H. S., Karpoff, M., Ochoa, E., Redshaw, M., \& Rodrigues, R. E.
        (2018).
        The Alberta Workloads for the SPEC CPU 2017 Benchmark Suite.
        \textit{Proceedings of the 2018 IEEE International Symposium on Performance Analysis of Systems and Software,} 159--168.
        \url{https://doi.org/10.1109/ISPASS.2018.00029}
\end{rPublications}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PREPRINTS AND TECHNICAL REPORTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Preprints and Technical Reports}

\begin{rPublications}
    \item
        {\v{S}}trupl, M., Szehr, O., Faccio, F., \textbf{Ashley, D. R.}, Srivastava, R. K., \& Schmidhuber, J.
        (2025).
        \textit{On the Convergence and Stability of Upside-Down Reinforcement Learning, Goal-Conditioned Supervised Learning, and Online Decision Transformers.}
        \url{https://arxiv.org/abs/2502.05672}

        \vspace{-0.4em}
        Submitted to the Journal of Machine Learning Research (JMLR).
    \item
        Di Ventura, J., \textbf{Ashley, D. R.}, Herrmann, V., Faccio, F., \& Schmidhuber, J.
        (2025).
        \textit{Upside Down Reinforcement Learning with Policy Generators.}
        \url{https://arxiv.org/abs/2501.16288}

        \vspace{-0.4em}
        Presented at the 2025 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item
        Wang, W., Alyahya, H. A., \textbf{Ashley, D. R.}, Serikov, O., Khizbullin, D., Faccio, F., \& Schmidhuber, J.
        (2024).
        \textit{How to Correctly do Semantic Backpropagation on Language-based Agentic Systems.}
        \url{http://arxiv.org/abs/2412.03624}
    \item
        Herrmann, V.$^*$, \textbf{Ashley, D. R.}$^*$, \& Schmidhuber, J.
        (2024).
        \textit{Automatic Album Sequencing.}
        \url{https://arxiv.org/abs/2411.07772}

        \vspace{-0.4em}
        Presented as a late-breaking demo at the 2024 Conference of the International Society for Music Information Retrieval (ISMIR).
    \item
        Alhakami, M.$^*$, \textbf{Ashley, D. R.}$^*$, Dunham, J.$^*$, Dai, Y., Faccio, F., Feron, F., \& Schmidhuber, J.
        (2024).
        \textit{Towards an Extremely Robust Baby Robot With Rich Interaction Ability for Advanced Machine Learning Algorithms.}
        \url{https://arxiv.org/abs/2404.08093}

        \vspace{-0.4em}
        Presented as a late-breaking result at the 2024 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS).
    \item
        Stanic, A.$^*$, \textbf{Ashley, D.}, Serikov, O., Kirsch, L., Faccio, F., Schmidhuber, J., Hofmann, T., \& Schlag, I.$^*$
        (2023).
        \textit{The languini kitchen: Enabling language modelling research at different scales of compute.}
        \url{https://arxiv.org/abs/2309.11197}
    \item
        {\v{S}}trupl, M., Faccio, F., \textbf{Ashley, D. R.}, Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{Upside-Down Reinforcement Learning Can Diverge in Stochastic Environments With Episodic Resets.}
        \url{https://arxiv.org/abs/2205.06595}

        \vspace{-0.4em}
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item
        \textbf{Ashley, D. R.}, Arulkumaran, K., Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{Learning Relative Return Policies With Upside-Down Reinforcement Learning.}
        \url{https://arxiv.org/abs/2202.12742}

        \vspace{-0.4em}
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item
        Arulkumaran, K., \textbf{Ashley, D. R.}, Schmidhuber, J., \& Srivastava, R. K.
        (2022).
        \textit{All You Need Is Supervised Learning: From Imitation Learning to Meta-RL With Upside Down RL.}
        \url{https://arxiv.org/abs/2202.11960}

        \vspace{-0.4em}
        Presented at the 2022 Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM).
    \item
        \textbf{Ashley, D. R.}, Ghiassian, S., \& Sutton, R. S.
        (2021).
        \textit{Does the Adam optimizer exacerbate catastrophic forgetting?}
        \url{https://arxiv.org/abs/2102.07686}
    \item
        Ma, C., \textbf{Ashley, D. R.}, Wen, J., \& Bengio, Y.
        (2020).
        \textit{Universal successor features for transfer reinforcement learning.}
        \url{https://arxiv.org/abs/2001.04025}
\end{rPublications}

\end{rSection}

%----------------------------------------------------------------------------------------
%   INVITED TALKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited Talks}

\rLine{NeurIPS 2023 R0-FoMo Workshop}{New Orleans, US}{2023} \\
\rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2022} \\
\rLine{Alberta Machine Intelligence Institute Tea Time Talks}{Virtual}{2021} \\
\rLine{Canadian Association for Graduate Studies Conference}{Halifax, CA}{2019} \\
\rLine{IEEE Conference on Games}{London, GB}{2019} \\
\rLine{Chinese Graduate Students Association Workshop}{Edmonton, CA}{2019} \\
\rLine{Kindred}{Toronto, CA}{2018}

\end{rSection}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}

\rLine{Best-Paper Award}{NeurIPS 2023 R0-FoMo Workshop}{2023} \\
\rLine{Rising Star in AI Award}{King Abdullah University of Science and Technology}{2022} \\
\rLine{Queen Elizabeth II Graduate Scholarship}{University of Alberta (C\$10,800)}{2018} \\
\rLine{CGS-M}{Natural Science and Engineering Research Council of Canada (C\$17,500)}{2017} \\
\rLine{Walter H. Johns Graduate Fellowship}{University of Alberta (C\$5,800)}{2017} \\
\rLine{Science Graduate Scholarship}{University of Alberta (C\$2,000)}{2017} \\
\rLine{Kao Family Eisenco Scholarship}{University of Alberta (C\$1,200)}{2016} \\
\rLine{Jason Lang Scholarship}{University of Alberta (C\$1,000)}{2015} \\
\rLine{Suncor Energy Scholarship}{Suncor Energy (C\$1,800)}{2015} \\
\rLine{Jason Lang Scholarship}{University of Alberta (C\$1,000)}{2014} \\
\rLine{Suncor Energy Scholarship}{Suncor Energy (C\$1,800)}{2014}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service}

\rLine{Reviewer}{International Conference on Learning Representations}{2026} \\
\rLine{Reviewer}{AAAI Conference on Artificial Intelligence}{2026} \\
\rLine{Reviewer}{ICLR 2025 Workshop on World Models}{2025} \\
\rLine{Reviewer}{International Conference on Learning Representations}{2025} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2024} \\
\rLine{Reviewer}{NeurIPS Workshop on Aligning RL Experimentalists and Theorists}{2024} \\
\rLine{Reviewer}{International Conference on Artificial Neural Networks}{2024} \\
\rLine{Reviewer}{Machine Learning}{2024} \\
\rLine{Program Committee Member}{European Workshop on Reinforcement Learning}{2023} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2023} \\
\rLine{Reviewer}{ICML Workshop on Interactive Learning with Implicit Human Feedback}{2023} \\
\rLine{Reviewer}{Machine Learning}{2023} \\
\rLine{Faculty of Informatics Council}{Universit{\`{a}} della Svizzera italiana}{2022 -- 2023} \\
\rLine{Reviewer}{NeurIPS Workshop on Information-Theoretic Principles in Cognitive Systems}{2022} \\
\rLine{Reviewer}{NeurIPS Workshop on Reinforcement Learning for Real Life Workshop}{2022} \\
\rLine{Reviewer}{European Workshop on Reinforcement Learning}{2022} \\
\rLine{Mentoring Award Adjudication Panel}{University of Alberta}{2020} \\
\rLine{Equity, Diversity, and Inclusion Council}{Alberta Machine Intelligence Institute}{2019 -- 2020} \\
\rLine{Volunteer}{Campus Food Bank}{2019} \\
\rLine{Faculty of Graduate Studies and Research Council}{University of Alberta}{2018 -- 2019} \\
\rLine{Board Member}{Graduate Students' Association}{2018 -- 2019} \\
\rLine{Nominating Committee}{Graduate Students' Association}{2018 -- 2019} \\
\rLine{Council Member}{Graduate Students' Association}{2018 -- 2020}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SUPERVISING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Supervising}

\rLine{Jacopo di Ventura}{M.Sc. Student}{2023 -- 2024} \\
\rLine{James Jewitt}{High School Intern}{2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching}

\rLine{Teaching Assistant}{Machine Learning}{2024} \\
\rLine{Teaching Assistant}{Machine Learning}{2023} \\
\rLine{Teaching Assistant}{Machine Learning}{2022} \\
\rLine{Teaching Assistant}{Algorithms \& Data Structures}{2022} \\
\rLine{Teaching Assistant}{Machine Learning}{2021} \\
\rLine{Teaching Assistant}{Introduction to File and Database Management}{2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROFESSIONAL MEMBERSHIP SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Membership}

\rPlainLine{Association for Computing Machinery}{Since 2014} \\
\rPlainLine{Association for the Advancement of Artificial Intelligence}{Since 2018} \\
\rPlainLine{Institute of Electrical and Electronics Engineers}{Since 2019}

\end{rSection}

%----------------------------------------------------------------------------------------
%   CITIZENSHIP AND RESIDENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Citizenship and Residence}

\begin{tabular}{lll}
    \rPair{Canada}{Citizen} & \rPair{South Africa}{Citizen} & \rPair{Switzerland}{B Permit}
\end{tabular}

\end{rSection}

\clearpage

%----------------------------------------------------------------------------------------
%   NATURAL LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Natural Languages}

\begin{tabular}{ll}
    \rPair{English}{Native Speaker} & \rPair{French}{Moderate Fluency} \\
    \rPair{Italian}{Some Knowledge} & \rPair{Mandarin}{Some Knowledge}
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   PROGRAMMING LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Programming Languages}

\begin{tabular}{llll}
    \rPair{Python}{Expert} & \rPair{Bash}{Strong} & \rPair{C/C++}{Strong} & \rPair{\LaTeX}{Strong} \\
    \rPair{Java}{Intermediate} & \rPair{SQL}{Intermediate} & \rPair{HTML}{Basic} & \rPair{Lisp}{Basic} \\
    \rPair{Prolog}{Basic}
\end{tabular}

\end{rSection}

% %----------------------------------------------------------------------------------------
% %   CONFERENCE AND SUMMER SCHOOL ATTENDANCE SECTION
% %----------------------------------------------------------------------------------------
%
% \begin{rSection}{Conference and Summer School Attendance}
%
% \rLine{IEEE/RSJ International Conference on Intelligent Robots and Systems}{Hangzhou, CN}{2025} \\
% \rLine{International Conference on Machine Learning}{Vancouver, CA}{2025} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2025} \\
% \rLine{International Society for Music Information Retrieval Conference}{San Francisco, US}{2024} \\
% \rLine{European Workshop on Reinforcement Learning}{Toulouse, FR}{2024} \\
% \rLine{IEEE/RSJ International Conference on Intelligent Robots and Systems}{Abu Dhabi, AE}{2024} \\
% \rLine{CSCS Summer University on Effective High-Performance Computing}{Lugano, CH}{2024} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2024} \\
% \rLine{Neural Information Processing Systems}{New Orleans, US}{2023} \\
% \rLine{European Workshop on Reinforcement Learning}{Brussels, BE}{2023} \\
% \rLine{Belgium-Netherlands Workshop on Reinforcement Learning}{Leiden, NL}{2023} \\
% \rLine{International Conference on Machine Learning}{Honolulu, US}{2023} \\
% \rLine{International Conference on Learning Representations}{Kigali, RW}{2023} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2023} \\
% \rLine{Neural Information Processing Systems}{New Orleans, USA}{2022} \\
% \rLine{European Workshop on Reinforcement Learning}{Milan, IT}{2022} \\
% \rLine{Reinforcement Learning and Decision Making}{Providence, US}{2022} \\
% \rLine{KAUST Rising Stars in AI Symposium}{Thuwal, SA}{2022} \\
% \rLine{AAAI Conference on Artificial Intelligence}{Virtual}{2021} \\
% \rLine{Neural Information Processing Systems}{Virtual}{2020} \\
% \rLine{Canadian Association for Graduate Studies Conference}{Halifax, CA}{2019} \\
% \rLine{IEEE Conference on Games}{London, GB}{2019} \\
% \rLine{CIFAR Deep Learning and Reinforcement Learning Summer School}{Edmonton, CA}{2019} \\
% \rLine{Reinforcement Learning and Decision Making}{Montr{\'{e}}al, CA}{2019} \\
% \rLine{Chinese Graduate Students Association Workshop}{Edmonton, CA}{2019} \\
% \rLine{Reverse Expo}{Edmonton, CA}{2019} \\
% \rLine{Neural Information Processing Systems}{Montr{\'{e}}al, CA}{2018} \\
% \rLine{Artificial Intelligence and Interactive Digital Entertainment}{Edmonton, CA}{2018} \\
% \rLine{Uncertainty in Artificial Intelligence}{Monterey, US}{2018} \\
% \rLine{CIFAR Deep Learning and Reinforcement Learning Summer School}{Toronto, CA}{2018} \\
% \rLine{Accelerate AB}{Edmonton, CA}{2018}
%
% \end{rSection}

%----------------------------------------------------------------------------------------

\vfill
\begin{center}
    \large{\MakeUppercase{\bf References Available On Request}}
\end{center}

\end{document}
